\documentclass{article}
\usepackage{ucs}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[serbian]{babel}

\title{Luis fon An}
\author{dzoni223}
\date{November 2019}

\begin{document}

\maketitle

\section{Učenje}

Fon An je koristio mnoge neobične tehnike u svojoj nastavi koje su mu donele brojne nagrade Univerziteta u Karnegi Melonu. Jeseni 2008. godine započeo je novi kurs na Karnegi Melonu sa nazivom „Nauka mreža” (engl. Science of the Web). Kombinacija teorije grafova i društvenih nauka, kurs obrađuje teme od teorije mreža i teorije igara do teorija aukcije.

\begin{thebibliography}{9}
\bibitem{ref1}
    \textit{„Luis von Ahn”.}
\bibitem{ref2}
    \textit{„Teaching computers to read: Google acquires reCAPTCHA”. Google Official Blog.}
\bibitem{ref3}
    \textit{„Duke Ugrad Alum Profile: Luis von Ahn”.}
\bibitem{ref4}
    \textit{https://www.cs.cmu.edu/~biglou/LuisvonAhnCV.pdf}
\bibitem{ref5}
    \textit{Federoff, Stacey. „Duolingo CEO Luis von Ahn wins Lemelson prize from MIT”.}
\bibitem{ref6} 
    \textit{Robert J. Simmons. „Profile Luis von Ahn: ReCaptcha, games with a purpose”. XRDS: Crossroads, the ACM Magazine for Students.}
\bibitem{ref7}
    \textit{„MacArthur Fellows”.}
\bibitem{ref8}
    \textit{„Congratulations, Luis von Ahn”. Google Official Blog.}
\bibitem{ref9}
    \textit{„President Obama Honors Outstanding Early-Career Scientists”. The White House.}
\bibitem{ref10}
    \textit{„Los nuevos rostros del pensiamento iberoamericano”. FP.}
\bibitem{ref11} 
    \textit{„Luis von Ahn”.}
\bibitem{ref12} 
    \textit{Von Ahn, Luis; Blum, Manuel; Hopper, Nicholas J.; Langford, John). "CAPTCHA: Using Hard AI Problems for Security". Proceedings of the International Conference on the Theory and Applications of Cryptographic Techniques}
\bibitem{ref13}
    \textit{Von Ahn, L.; Blum, M.; Langford, J. „Telling humans and computers apart automatically”. Communications of the ACM.}
\bibitem{ref14}
    \textit{Von Ahn, L.; Dabbish, L. „Labeling images with a computer game”. Proceedings of the conference on Human factors in computing systems}
\bibitem{ref15}
    \textit{Von Ahn, L. „Games with a Purpose”.}
\bibitem{ref16} Google Tech Talk on human computation by Luis von Ahn.
\bibitem{ref17}
    \textit{„reCAPTCHA (a.k.a. Those Infernal Squiggly Words) Almost Done Digitizing the New York Times Archive”. Blog.newsweek.com.}
\bibitem{ref18}
    \textit{Habermmann Chair announcement. News.cs.cmu.edu}
\bibitem{ref19}
    \textit{Federoff, Stacey. „Duolingo CEO Luis von Ahn wins Lemelson prize from MIT”. TribLIVE.com.}
\bibitem{ref20}
    \textit{Duolingo.com}
\bibitem{ref21}
    \textit{CMU Faculty Awards.}
\bibitem{ref22}
    \textit{„Science of the Web”. Andrew.cmu.edu.}
\end{thebibliography}

\end{document}
